\documentclass[10pt]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\setlist[itemize]{leftmargin=*, noitemsep, topsep=2pt, parsep=0pt}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\titlespacing{\section}{0pt}{6pt}{3pt}
\hypersetup{hidelinks}

\begin{document}

\begin{center}
{\Large \textbf{SANGRAMJEET GHOSH}} \\[2pt]
{\small +91 9059150937 \;|\; sangramjeet47@gmail.com \;|\;
\href{https://www.linkedin.com/in/sangramjeetghosh}{linkedin.com/in/sangramjeetghosh} \;|\;
\href{https://github.com/JeetInTech}{github.com/JeetInTech} \;|\;
\href{https://neuroviai.com}{neuroviai.com}}
\end{center}

\noindent\rule{\textwidth}{0.4pt}

\section*{SUMMARY}
Backend-focused AI Systems Engineer with hands-on experience building production-grade multi-agent workflows, LLM orchestration layers, and deterministic validation pipelines using Python and FastAPI. Strong foundation in system design, async API architecture, PostgreSQL schema design, and microservice reliability. Experienced in integrating LLM APIs with rule-based validation, structured outputs, and stateful memory for real-world AI applications.

\section*{CORE SKILLS}
\textbf{Languages:} Python, SQL, JavaScript (working knowledge) \\
\textbf{AI Systems:} LangGraph, LangChain, RAG Pipelines, Prompt Engineering, Structured JSON Enforcement, Multi-Model Orchestration \\
\textbf{Backend:} FastAPI, REST API Design, Async/Await, Middleware, Webhooks, Background Tasks \\
\textbf{Databases:} PostgreSQL, Supabase, Redis (basics), Schema Design, Indexing \\
\textbf{Infrastructure:} Docker, AWS (EC2, S3, IAM), GitHub Actions CI/CD, Render \\
\textbf{Engineering Practices:} Idempotency, Retry Backoff, Error Handling, Logging, Input Validation

\section*{EXPERIENCE}

\textbf{Data Science Intern -- Inikola Technologies} \hfill Mar 2025 \\
Hyderabad
\begin{itemize}
\item Developed FastAPI-based backend services powering production NLP features for a live content platform.
\item Built data ingestion and processing pipelines for real-time text analysis and scoring.
\item Managed AWS EC2 deployments, IAM policies, S3 storage, and Nginx reverse proxy configuration.
\item Containerized services using Docker and implemented CI/CD pipelines for automated deployment.
\item Authored technical documentation covering architecture decisions, deployment workflows, and failure handling.
\end{itemize}

\textbf{Freelance AI / Backend Developer} \hfill Aug 2025 -- Present \\
Remote
\begin{itemize}
\item Designed API-first backend systems using FastAPI with JWT authentication, role-based access control, and webhook processors.
\item Implemented idempotent transaction handlers and structured logging for production reliability.
\item Built async integrations with third-party APIs including OAuth flows, token refresh, and rate-limit handling.
\item Delivered containerized microservices with documented API contracts and schema validation.
\end{itemize}

\section*{PROJECTS}

\textbf{Neuroviai -- Multi-Service AI Automation Platform} \\
\textit{FastAPI, PostgreSQL, Docker, LLM APIs} \;|\;
\href{https://neuroviai.com}{neuroviai.com}
\begin{itemize}
\item Architected backend as independent microservices: authentication, AI inference, content orchestration, and billing.
\item Designed multi-model LLM routing layer with structured JSON schema validation and fallback logic for provider resilience.
\item Implemented async API orchestration with retry backoff, rate-limit handling, and token lifecycle management.
\item Built stateful session tracking and usage logging in PostgreSQL with indexed relational schemas.
\item Developed webhook-based event processors with idempotency guarantees and transaction reconciliation.
\end{itemize}

\textbf{Virtual Therapist -- Agentic AI System} \\
\textit{LangGraph, LangChain, Python, PostgreSQL} \;|\;
\href{https://github.com/JeetInTech/Virtual-Therapist---LangGraph-Agentic-AI-System}{GitHub}
\begin{itemize}
\item Designed a stateful 3-agent workflow using LangGraph: intake agent, emotion analysis agent, and response synthesis agent.
\item Implemented deterministic state transitions with structured prompt contracts and JSON output validation.
\item Persisted conversation memory and session context in PostgreSQL for long-running interactions.
\item Built FastAPI endpoints for speech-to-text ingestion and LLM-driven response generation.
\item Containerized system using Docker Compose with isolated services and environment configuration.
\end{itemize}

\section*{EDUCATION}
\textbf{B.Tech in Computer Science and Engineering (AI \& ML)} \hfill Expected 2026 \\
Malla Reddy University, Hyderabad \hfill GPA: 8.0 / 10.0

\end{document}