\documentclass[9.5pt]{article}
\usepackage[margin=0.4in, top=0.35in, bottom=0.35in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{array}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}

\setlist[itemize]{leftmargin=1.2em, noitemsep, topsep=1pt, parsep=0pt}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\titlespacing{\section}{0pt}{4pt}{1.5pt}
\titleformat{\section}{\bfseries\uppercase}{}{0pt}{}[\titlerule]
\hypersetup{hidelinks}
\newcolumntype{L}{>{\raggedright\arraybackslash}X}

\begin{document}

% ===== HEADER =====
\begin{center}
  {\large \textbf{SANGRAMJEET GHOSH}} \\[2pt]
  {\small
    +91~9059150937 \;|\;
    \href{mailto:sangramjeet47@gmail.com}{sangramjeet47@gmail.com} \;|\;
    \href{https://www.linkedin.com/in/sangramjeetghosh}{linkedin.com/in/sangramjeetghosh} \;|\;
    \href{https://github.com/JeetInTech}{github.com/JeetInTech} \;|\;
    \href{https://sangramjeet.me}{sangramjeet.me} \;|\;
    \href{https://neuroviai.com}{neuroviai.com}
  }
\end{center}

\vspace{-2pt}
\noindent\rule{\textwidth}{0.4pt}
\vspace{-4pt}

% ===== SUMMARY =====
\section*{Summary}
Full-Stack Engineer with production experience shipping scalable web applications, AI systems, and automation pipelines. Skilled in Python, TypeScript, React, and Next.js, with a strong focus on frontend and backend development. Proficient in designing and implementing scalable backend services, optimizing algorithms, and collaborating with cross-functional teams.

% ===== SKILLS =====
\section*{Skills}
\begin{tabularx}{\textwidth}{@{} p{1.9cm} X @{}}
\textbf{Languages}  & Python, TypeScript, JavaScript, SQL, Bash \\[1pt]
\textbf{Frontend}    & React 18, Next.js 14, HTML5 Canvas, Pixi.js, Redux, Tailwind CSS \\[1pt]
\textbf{Backend}     & FastAPI, REST APIs, WebSockets, JWT/OAuth 2.0, Webhooks, Microservices, Async Python \\[1pt]
\textbf{Databases}   & PostgreSQL, MySQL, Redis, SQLAlchemy, pgvector \\[1pt]
\textbf{DevOps}       & Docker, GitHub Actions CI/CD, AWS (EC2, S3, IAM), Render, Netlify, Nginx, FFmpeg \\
\end{tabularx}

% ===== EXPERIENCE =====
\section*{Experience}

\textbf{Freelance AI \& Full-Stack Developer} \hfill \textit{Aug 2025 -- Present} \quad \textit{Remote}
\begin{itemize}
  \item Designed and developed scalable web applications using React, Next.js, and FastAPI, with a focus on optimization and performance.
  \item Collaborated with clients to deliver high-quality solutions, providing technical guidance and support.
\end{itemize}

\vspace{1.5pt}
\textbf{Data Science Intern --- Inikola Technologies, Hyderabad} \hfill \textit{Mar 2025 -- Dec 2025}
\begin{itemize}
  \item Built FastAPI NLP pipelines for sentiment scoring and topic extraction, utilizing AWS infrastructure and Docker containerization.
  \item Managed AWS resources, including EC2, S3, and IAM, and deployed CI/CD pipelines using GitHub Actions.
\end{itemize}

% ===== PROJECTS =====
\section*{Projects}

\textbf{Neuroviai --- AI Social Media Automation SaaS} \hfill \textit{Mar 2025 -- Present} \quad \href{https://neuroviai.com}{neuroviai.com}\\
\textit{Next.js 14, FastAPI, PostgreSQL, Supabase, Gemini, OpenAI, Razorpay, Docker}
\begin{itemize}
  \item Designed and implemented a scalable backend service using FastAPI and PostgreSQL, with a focus on optimization and performance.
  \item Integrated multiple APIs, including LinkedIn, Twitter, and Razorpay, using OAuth flows and rate-limit handling.
\end{itemize}

\vspace{1.5pt}
\textbf{AI YouTube Shorts Automation Pipeline} \hfill \textit{Jan 2026 -- Present} \quad \href{https://github.com/JeetInTech/Youtube-shorts-Automation}{GitHub}\\
\textit{Python, Ollama (local LLM), FFmpeg, edge-tts, Pexels API, YouTube Data API v3}
\begin{itemize}
  \item Built an end-to-end pipeline for automating YouTube Shorts creation, utilizing Python, FFmpeg, and the YouTube Data API.
  \item Optimized the pipeline for performance and scalability, using asynchronous programming and distributed systems.
\end{itemize}

% ===== EDUCATION =====
\section*{Education}
\textbf{B.Tech in Computer Science \& Engineering (AI \& ML)} \hfill \textit{Expected June 2026}\\
Malla Reddy University, Hyderabad \hfill GPA: 8.0\,/\,10.0

\end{document}