\documentclass[11pt]{article}
\usepackage[margin=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}

\setlist[itemize]{leftmargin=*, noitemsep, topsep=3pt, parsep=1pt}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\titlespacing{\section}{0pt}{10pt}{5pt}
\titleformat{\section}{\large\bfseries\scshape}{}{0pt}{}[\titlerule]
\hypersetup{colorlinks=true, urlcolor=blue!70!black, linkcolor=blue!70!black}

\begin{document}

% ===== HEADER =====
\begin{center}
{\LARGE \textbf{SANGRAMJEET GHOSH}} \\[6pt]
{\normalsize
  +91 9059150937 \quad $|$ \quad
  \href{mailto:sangramjeet47@gmail.com}{sangramjeet47@gmail.com} \quad $|$ \quad
  \href{https://www.linkedin.com/in/sangramjeetghosh}{linkedin.com/in/sangramjeetghosh}
}\\[2pt]
{\normalsize
  \href{https://github.com/JeetInTech}{github.com/JeetInTech} \quad $|$ \quad
  \href{https://sangramjeet.me}{sangramjeet.me} \quad $|$ \quad
  \href{https://neuroviai.com}{neuroviai.com} \quad $|$ \quad
  \href{https://drive.google.com/drive/folders/1ZQd-DeX-rXlEVDTwDJfjLjnG7iPc_fEw}{Certificates Portfolio}
}
\end{center}

\vspace{2pt}

% ===== PROFESSIONAL SUMMARY =====
\section*{Professional Summary}

Versatile AI \& Full-Stack Engineer with hands-on experience building and shipping production-grade SaaS platforms, autonomous AI systems, and content automation pipelines. Designed and launched Neuroviai — a live multi-provider LLM automation SaaS. Built Sebastian, a fully autonomous assistant with real-time voice, vision, OS control, and 110+ API integrations. Applied AI researcher specializing in constraint-driven system design with proven ability to take products from concept to deployment across cloud platforms. Actively seeking opportunities to build impactful, scalable technology.

% ===== EDUCATION =====
\section*{Education}

\textbf{Bachelor of Technology (B.Tech) in Computer Science and Engineering} \hfill \textit{Expected June 2026} \\
Specialization in Artificial Intelligence and Machine Learning \\
Malla Reddy University, Hyderabad, Telangana \hfill \textbf{GPA: 8.0 / 10.0}

\begin{itemize}
\item \textbf{Relevant Coursework:} Data Structures \& Algorithms, Machine Learning, Deep Learning, Natural Language Processing, Computer Vision, Database Management Systems, Cloud Computing, Statistics \& Probability
\item \textbf{Thesis:} \textit{Design and Implementation of Cost-Constrained AI Automation Systems} (Feb 2026) --- Full-stack SaaS platform (Neuroviai) with 15,000+ lines of Python and 12,000+ lines of TypeScript; regulatory-aligned data stewardship (India's DPDPA 2023, EU AI Act).
\end{itemize}

% ===== TECHNICAL SKILLS =====
\section*{Technical Skills}

\begin{tabularx}{\textwidth}{@{} p{2.6cm} X @{}}
\textbf{Languages}     & Python, JavaScript, TypeScript, SQL, HTML5, CSS3, Bash \\[3pt]
\textbf{AI / ML}       & LangChain, LangGraph, Gemini API, OpenAI API, Groq, RAG Pipelines, pgvector, Prompt Engineering, Multi-Agent Systems, Scikit-learn, XGBoost, LightGBM, Pandas, NumPy \\[3pt]
\textbf{Backend}       & FastAPI, REST APIs, WebSockets, JWT/OAuth 2.0, Webhook Handlers, Microservices Architecture, Async Python \\[3pt]
\textbf{Frontend}      & React 18, Next.js 14 (App Router), Tailwind CSS, Zustand, ShadCN/UI, Vite, TypeScript \\[3pt]
\textbf{Databases}     & PostgreSQL, Supabase, pgvector, MongoDB (basics), Redis, SQLAlchemy ORM \\[3pt]
\textbf{DevOps/Cloud}  & AWS (EC2, S3, IAM), Docker, Docker Compose, GitHub Actions CI/CD, Render, Vercel, Netlify, Nginx, FFmpeg \\[3pt]
\textbf{Tools}         & Git, GitHub, Postman, VS Code, Playwright, PyAutoGUI \\
\end{tabularx}

% ===== WORK EXPERIENCE =====
\section*{Work Experience}

\textbf{Freelance AI \& Full-Stack Developer} \hfill \textit{Aug 2025 -- Present} \\
\textit{Remote}
\begin{itemize}
  \item Delivered end-to-end web applications and AI-powered MVPs for 3+ startup founders, handling requirements gathering, architecture design, development, deployment, and post-launch iteration.
  \item Built SaaS products with subscription billing (Razorpay), role-based access control (JWT/OAuth), and multi-platform API integrations.
  \item Deployed applications across AWS, Render, Vercel, and Netlify with custom domains, SSL certificates, and CDN configuration.
  \item Managed LLM provider costs through intelligent quota splitting, response caching, and request batching strategies.
  \item Created integration guides and handoff documentation enabling clients' in-house teams to maintain and extend delivered products.
\end{itemize}

\vspace{4pt}
\textbf{Data Science Intern --- Inikola Technologies} \hfill \textit{Mar 2025 -- Dec 2025} \\
\textit{Hyderabad}
\begin{itemize}
  \item Developed AI-powered backend features for CraftingBrain (\href{https://craftingbrain.com}{craftingbrain.com}), a live content-technology platform, using Python and FastAPI.
  \item Built and deployed NLP pipelines for real-time text analysis, sentiment scoring, topic extraction, and content optimization in production environments.
  \item Managed AWS infrastructure: EC2 provisioning, S3 bucket policies, IAM role configuration, and Nginx reverse-proxy setup.
  \item Containerized Python services using multi-stage Docker builds, reducing image size and cold-start latency.
  \item Authored CI/CD pipelines with GitHub Actions automating linting, testing, and zero-downtime production deployments.
\end{itemize}

% ===== PROJECTS =====
\section*{Projects}

\textbf{Neuroviai --- AI-Powered Social Media Automation SaaS} \hfill \textit{Mar 2025 -- Present} \\
\textit{Next.js 14, FastAPI, PostgreSQL, Supabase, Gemini, OpenAI, Razorpay, Docker} \hfill \href{https://neuroviai.com}{neuroviai.com}
\begin{itemize}
  \item Designed and built a full-stack AI SaaS platform from scratch --- product design, database schema, API architecture, AI pipelines, payment integration, and multi-platform publishing.
  \item Architected 4-tier LLM cascade (Gemini $\rightarrow$ GROQ $\rightarrow$ HuggingFace) achieving 99.7\% text generation reliability; autonomous engine posts across 5 platforms daily, cutting operational effort by 90\%.
  \item Integrated 8+ external APIs (LinkedIn Publishing, Twitter/X, Razorpay, Supabase Auth) with OAuth flows, webhook listeners, error handling, and rate-limit management.
  \item Designed token-economy billing: per-user credit tracking, usage alerts, low-balance upsell triggers, and plan-upgrade flows.
  \item Deployed as 4 microservices (Render, Supabase, Netlify, AWS S3) with GitHub Actions CI/CD and engagement analytics dashboard.
\end{itemize}

\vspace{4pt}
\textbf{Sebastian --- Autonomous AI Personal Assistant} \hfill \textit{Jan 2026 -- Present} \\
\textit{Python, FastAPI, PostgreSQL, pgvector, Gemini Live, Groq, Playwright, Edge TTS, PyAutoGUI}
\begin{itemize}
  \item Architected a 10-phase fully autonomous assistant with 59+ tools across OS control, browser automation, real-time bidirectional audio streaming (Gemini Live), camera/screen vision, and 110+ API integrations.
  \item Built a multi-layer memory system (episodic, semantic, behavioral) using PostgreSQL + pgvector with cosine similarity search, time-decay importance weighting, and automatic memory deduplication.
  \item Implemented a 3-tier permission gate (GREEN/YELLOW/RED) with automatic escalation and full audit logging for every tool execution.
  \item Added Discord voice channel bridge via py-cord with real-time PCM audio resampling between Discord (48kHz stereo) and the Gemini Live pipeline (16kHz mono).
  \item Exposed a FastAPI server with REST + WebSocket endpoints and a React PWA dashboard for cross-device access.
\end{itemize}

\vspace{4pt}
\textbf{AI YouTube Shorts Automation Pipeline} \hfill \textit{Jan 2026 -- Present} \\
\textit{Python, Ollama (local LLM), FFmpeg, edge-tts, Pexels API, YouTube Data API v3} \hfill \href{https://github.com/JeetInTech/Youtube-shorts-Automation}{GitHub}
\begin{itemize}
  \item Built a fully automated short-form video pipeline: trend scraping (Reddit, Hacker News, Google Trends) $\rightarrow$ LLM script generation with quality scoring $\rightarrow$ voiceover synthesis $\rightarrow$ stock footage assembly (FFmpeg) $\rightarrow$ YouTube upload with metadata.
  \item Engineered Windows Task Scheduler integration for unattended daily posting; multi-channel mode generates 4+ videos per run.
  \item Implemented a script quality scoring module to filter low-confidence AI scripts before production, with a Streamlit analytics dashboard for tracking upload history and performance metrics.
\end{itemize}

\vspace{4pt}
\textbf{Neurovia Careers --- AI-Powered ATS Resume Builder} \hfill \textit{Nov 2025 -- Present} \\
\textit{React 18, TypeScript, FastAPI, Supabase, Groq LLM, Vite} \hfill \href{https://github.com/JeetInTech/CvForge-Online}{GitHub}
\begin{itemize}
  \item Built a full-stack ATS resume builder with a weighted scoring engine: keyword match (40\%), content completeness (35\%), formatting quality (25\%) targeting 90\%+ ATS compatibility across 15+ job categories.
  \item Engineered a custom LaTeX export system with 4 professional templates (Simple, ModernCV, Awesome-CV, Deedy) producing clean, recruiter-safe PDFs.
  \item Integrated Groq LLM API for AI-assisted bullet generation, summary writing, and skill recommendations with Supabase auth, cloud CV storage, and shareable CV links.
\end{itemize}

\vspace{4pt}
\textbf{NeuroviaI --- Multi-Agent AI Data Analytics Platform} \hfill \textit{Oct 2025 -- Present} \\
\textit{Python, PySide6 (Qt6), Groq, Gemini, Ollama, Scikit-learn, XGBoost, LightGBM, Matplotlib}
\begin{itemize}
  \item Developed a desktop analytics platform using a 6-agent LLM pipeline (Profiler, Cleaner, Feature Engineer, Model Selector, Visualizer, Orchestrator) each executing think $\rightarrow$ act $\rightarrow$ observe loops.
  \item Benchmarked 11 ML models (Random Forest, XGBoost, LightGBM, SVM, etc.) with cross-validation and automated feature importance analysis.
  \item Built 20+ chart types (2D + 3D with matplotlib) across 5 themeable styles; implemented LLM provider failover: Groq $\rightarrow$ Gemini $\rightarrow$ Ollama for full offline capability.
\end{itemize}

\vspace{4pt}
\textbf{Virtual Therapist --- LangGraph Agentic AI System} \hfill \textit{Sep -- Oct 2025} \\
\textit{LangGraph, LangChain, Python, PostgreSQL} \hfill \href{https://github.com/JeetInTech/Virtual-Therapist---LangGraph-Agentic-AI-System}{GitHub}
\begin{itemize}
  \item Designed a stateful 3-agent LangGraph system (intake, emotion-detection, therapeutic-response) with deterministic state transitions, structured prompt contracts, and JSON output validation.
  \item Integrated speech-to-text input and adaptive LLM responses tuned to detected emotional context; persisted conversation memory in PostgreSQL.
\end{itemize}

% ===== PUBLICATIONS & RESEARCH =====
\section*{Publications \& Research}

\textbf{Design and Implementation of a Cost-Constrained Multi-Platform AI Automation System} \\
\textit{Independent Researcher --- Manuscript in Preparation (Case Study on Neuroviai)}
\begin{itemize}
  \item Engineered a deterministic four-tier AI fallback strategy (Gemini, GROQ, HuggingFace) achieving 99.7\% text generation reliability through provider-level redundancy.
  \item Documented orchestration-free microservice patterns to maximize free-tier resource allocations across ten independent server processes.
  \item Formalized 23 distinct engineering trade-offs regarding cold-start mitigation, ephemeral storage, and security in zero-budget environments.
\end{itemize}

% ===== ACHIEVEMENTS =====
\section*{Achievements \& Recognition}

\begin{itemize}
  \item \textbf{Winner --- IDEATHON 2.0} (University-level Ideation Competition): Developed a high-impact AI solution evaluated by industry experts for technical execution, feasibility, and market potential.
  \item \textbf{Participant --- METALLOOP 2K23} (National-level Hackathon): Built a functional prototype under intensive time constraints; received official certification for technical execution.
  \item \textbf{Self-Published Author --- Amazon KDP:} Authored \textit{``The Future of Touchless Technology;''} managed end-to-end digital publishing lifecycle including automated manuscript formatting and global distribution. \href{https://www.amazon.com/dp/B0FBLC1RLT}{amazon.com/dp/B0FBLC1RLT}
\end{itemize}

% ===== CERTIFICATIONS =====
\section*{Certifications}
\textit{All certificates verified and available at:} \href{https://drive.google.com/drive/folders/1ZQd-DeX-rXlEVDTwDJfjLjnG7iPc_fEw}{\textbf{Certificate Portfolio (Google Drive)}}

\begin{itemize}
  \item \textbf{Amazon Web Services (AWS)} --- Cloud Practitioner Essentials / Foundations
  \item \textbf{Google Cloud} --- Cloud Computing Fundamentals
  \item \textbf{Coursera} --- Machine Learning Specialization / AI \& Data Science tracks
  \item \textbf{Microsoft Learn} --- Azure AI Fundamentals / Developer certifications
  \item \textbf{NPTEL} --- Programming and Data Science courses (IIT-certified)
\end{itemize}

% ===== EXTRACURRICULAR =====
\section*{Extracurricular \& Leadership}
\begin{itemize}
  \item \textbf{Open-Source Contributor:} Actively maintain public repositories on GitHub (\href{https://github.com/JeetInTech}{github.com/JeetInTech}) with multiple AI, web, and data projects.
  \item \textbf{Technical Mentor:} Guide junior students in AI/ML concepts, project development, and hackathon preparation.
  \item \textbf{Hackathon Participant:} Regular competitor in national-level hackathons; strong track record of building functional prototypes under 24--48 hour deadlines.
  \item \textbf{Freelance Consultant:} Advise early-stage startup founders on technology stack selection, architecture design, and MVP scoping.
\end{itemize}

% ===== LANGUAGES =====
\section*{Languages}
English (Professional Proficiency) \quad $|$ \quad Hindi (Native) \quad $|$ \quad Bengali (Native)

\vfill
\begin{center}
  \small\textit{References available upon request.}
\end{center}

\end{document}
