\documentclass[10pt]{article}
\usepackage[margin=0.4in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\setlist[itemize]{leftmargin=*, noitemsep, topsep=2pt, parsep=0pt}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\titlespacing{\section}{0pt}{6pt}{3pt}
\hypersetup{hidelinks}

\begin{document}

\begin{center}
{\Large \textbf{SANGRAMJEET GHOSH}} \\[2pt]
{\small +91 9059150937 $|$ sangramjeet47@gmail.com $|$
\href{https://www.linkedin.com/in/sangramjeetghosh}{linkedin.com/in/sangramjeetghosh} $|$
\href{https://github.com/JeetInTech}{github.com/JeetInTech} $|$
\href{https://neuroviai.com}{neuroviai.com}}
\end{center}

\noindent\rule{\textwidth}{0.4pt}

\section*{ABOUT}
Frontend engineer who builds fast, accessible, and responsive interfaces with React and Next.js 14. Fluent in TypeScript, component-driven architecture, Tailwind CSS utility styling, and Zustand state management. Shipped a cross-platform SaaS dashboard (web + Capacitor mobile) with real-time analytics, content calendars, and multi-platform publishing views.

\section*{FRONTEND TOOLKIT}
\textbf{Frameworks:} React 18, Next.js 14 (App Router, SSR, RSC), TypeScript, Vite \\
\textbf{Styling:} Tailwind CSS, CSS3, Flexbox, Grid, Mobile-First, Responsive Breakpoints \\
\textbf{State \& Data:} Zustand, React Context, SWR/React Query patterns, REST consumption \\
\textbf{Mobile \& Perf:} Capacitor, PWA, Code Splitting, Lazy Loading, Core Web Vitals, SEO

\section*{PROJECTS -- WHAT I BUILT}
\textbf{Neuroviai Dashboard} $|$ \textit{Next.js 14, TypeScript, Tailwind, Zustand} $|$ \href{https://neuroviai.com}{neuroviai.com}
\begin{itemize}
\item Designed and coded the entire SaaS frontend: onboarding wizard, analytics dashboard, content scheduler, settings panel.
\item Built reusable component library (buttons, modals, toasts, tables) with Tailwind utility classes and design tokens.
\item Managed global state via Zustand stores for auth session, content queue, notifications, and theme toggling.
\item Shipped Capacitor mobile build for Android/iOS maintaining full feature parity with the web app.
\item Achieved 90+ Lighthouse score through image optimization, route-level code splitting, and meta tag management.
\end{itemize}

\textbf{CvForge -- Resume Builder UI} $|$ \textit{HTML5, CSS3, JavaScript} $|$ \href{https://github.com/JeetInTech/CvForge-Online}{GitHub}
\begin{itemize}
\item Crafted interactive form UI with live preview, template switching, drag-and-drop sections, and instant PDF export.
\item Ensured cross-browser compatibility and responsive layout from mobile to wide-screen.
\end{itemize}

\textbf{Therapy Chat Interface} $|$ \textit{React, WebSocket} $|$ \href{https://github.com/JeetInTech/Virtual-Therapist---LangGraph-Agentic-AI-System}{GitHub} \hfill Sep--Oct 2025
\begin{itemize}
\item Built real-time chat UI with message streaming, typing indicators, and speech-to-text input toggle.
\end{itemize}

\section*{EXPERIENCE}
\textbf{Inikola Technologies -- Data Science Intern} \hfill Mar 2025 -- Present
\begin{itemize}
\item Designed interactive UI components and data-visualisation views for the CraftingBrain product.
\item Connected frontend to REST APIs with loading skeletons, error boundaries, and client-side caching.
\item Collaborated on production launch of craftingbrain.com focusing on responsive polish and performance.
\end{itemize}

\textbf{Freelance Frontend Developer} \hfill Nov 2024 -- Present
\begin{itemize}
\item Delivered pixel-perfect, mobile-first interfaces for startup clients using Next.js and Tailwind CSS.
\item Implemented protected routes, JWT token handling, and OAuth consent screens on the client side.
\item Converted Figma mockups into accessible, semantic HTML with ARIA attributes where needed.
\end{itemize}

\section*{EDUCATION}
\textbf{B.Tech, AI \& Machine Learning} -- Malla Reddy University \hfill Expected 2026 \hfill GPA: 8.0/10

\section*{AWARDS}
1st Place IDEATHON 2.0 $|$ METALLOOP 2K23 Hackathon $|$ Coursera, Google Cloud, Microsoft Learn, NPTEL, AWS Certs

\end{document}
