\documentclass[10pt]{article}
\usepackage[margin=0.4in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\setlist[itemize]{leftmargin=*, noitemsep, topsep=2pt, parsep=0pt}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\titlespacing{\section}{0pt}{6pt}{3pt}
\hypersetup{hidelinks}

\begin{document}

\begin{center}
{\Large \textbf{SANGRAMJEET GHOSH}} \\[2pt]
{\small +91 9059150937 $|$ sangramjeet47@gmail.com $|$
\href{https://www.linkedin.com/in/sangramjeetghosh}{linkedin.com/in/sangramjeetghosh} $|$
\href{https://github.com/JeetInTech}{github.com/JeetInTech} $|$
\href{https://neuroviai.com}{neuroviai.com}}
\end{center}

\noindent\rule{\textwidth}{0.4pt}

\section*{SUMMARY}
Software Engineer with solid CS fundamentals and real shipping experience across frontend, backend, databases, AI, and cloud. Comfortable picking up new stacks quickly. Solo-built and launched a production SaaS product---from database schema to payment checkout to cloud deploy. Published IEEE research paper. Strong at writing clean, maintainable, well-documented code.

\section*{TECHNICAL SKILLS}
\textbf{Languages:} Python, JavaScript, TypeScript, SQL \\
\textbf{Web:} React, Next.js 14, FastAPI, REST APIs, HTML5, CSS3, Tailwind CSS \\
\textbf{Data:} PostgreSQL, Supabase, MySQL, Schema Design, Indexing \\
\textbf{AI:} LLM Integration, Prompt Engineering, NLP, LangGraph, RAG \\
\textbf{Tools:} Docker, AWS, Git, GitHub Actions, CI/CD, Postman, Render, Netlify

\section*{EXPERIENCE}
\textbf{Inikola Technologies -- Data Science Intern} \hfill Mar 2025 -- Present
\begin{itemize}
\item Built Python/FastAPI services and React UI for the CraftingBrain platform; code reviewed by senior engineers.
\item Integrated NLP text-processing modules and exposed results through documented REST endpoints.
\item Participated in sprint planning, wrote unit tests, and maintained Git branching discipline.
\end{itemize}

\textbf{Freelance Software Developer} \hfill Nov 2024 -- Present
\begin{itemize}
\item Delivered 3+ production apps covering auth, payments, API integrations, and responsive frontends.
\item Wrote clean, modular code with separation of concerns, docstrings, and structured error handling.
\item Gathered client requirements, proposed architectures, and owned delivery through production go-live.
\end{itemize}

\section*{PROJECTS}
\textbf{Neuroviai -- AI SaaS Platform} $|$ \textit{Next.js, FastAPI, PostgreSQL} $|$ \href{https://neuroviai.com}{neuroviai.com}
\begin{itemize}
\item Solo-engineered a live SaaS: auth system, subscription billing (Razorpay), AI content engine, analytics dashboard.
\item Integrated 8 third-party APIs with OAuth flows, webhook handling, and graceful error recovery.
\item Deployed microservices across AWS, Render, Netlify with Docker containers and CI/CD automation.
\end{itemize}

\textbf{CvForge -- Resume Builder} $|$ \textit{JavaScript, FastAPI} $|$ \href{https://github.com/JeetInTech/CvForge-Online}{GitHub}
\begin{itemize}
\item Built full-stack web app: dynamic forms, live preview, template engine, and PDF export endpoint.
\end{itemize}

\textbf{Virtual Therapist} $|$ \textit{Python, LangGraph} $|$ \href{https://github.com/JeetInTech/Virtual-Therapist---LangGraph-Agentic-AI-System}{GitHub} \hfill Sep--Oct 2025
\begin{itemize}
\item Created multi-agent AI system with speech input, emotional-context detection, and guided conversation flows.
\end{itemize}

\section*{EDUCATION}
\textbf{B.Tech, AI \& Machine Learning} -- Malla Reddy University \hfill Expected 2026 \hfill GPA: 8.0/10

\section*{ACHIEVEMENTS}
IEEE Research Paper Published $|$ 1st Place IDEATHON 2.0 $|$ METALLOOP 2K23 National Hackathon \\
\textit{Certs:} Coursera, Microsoft Learn, Google Cloud, NPTEL, AWS

\end{document}
