\documentclass[10pt]{article}
\usepackage[margin=0.4in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\setlist[itemize]{leftmargin=*, noitemsep, topsep=2pt, parsep=0pt}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\titlespacing{\section}{0pt}{6pt}{3pt}
\hypersetup{hidelinks}

\begin{document}

\begin{center}
{\Large \textbf{SANGRAMJEET GHOSH}} \\[2pt]
{\small +91 9059150937 $|$ sangramjeet47@gmail.com $|$
\href{https://www.linkedin.com/in/sangramjeetghosh}{linkedin.com/in/sangramjeetghosh} $|$
\href{https://github.com/JeetInTech}{github.com/JeetInTech} $|$
\href{https://neuroviai.com}{neuroviai.com}}
\end{center}

\noindent\rule{\textwidth}{0.4pt}

\section*{SUMMARY}
AI Application Developer who puts language models into production products---not just Jupyter notebooks. Specializes in multi-model orchestration, prompt engineering, RAG retrieval, and image generation inside real web apps. Built and shipped a live SaaS with multi-provider LLM routing, fallback chains, quota management, and token-economy billing. IEEE-published researcher.

\section*{AI APPLICATION SKILLS}
\textbf{LLM Ops:} Multi-Model Routing, Prompt Templates, Structured Output Parsing, Fallback Chains \\
\textbf{Retrieval:} RAG Pipelines, Vector Search, Embeddings (OpenAI, Gemini), Contextual Reranking \\
\textbf{Agents:} LangGraph, LangChain, Multi-Agent Orchestration, Tool Calling \\
\textbf{NLP:} Sentiment Analysis, Text Classification, Named Entity Recognition, Transformers \\
\textbf{Stack:} Python, FastAPI, PostgreSQL, Next.js, Docker, AWS

\section*{PROJECTS -- SHIPPED AI PRODUCTS}
\textbf{Neuroviai -- AI Content Engine} $|$ \textit{FastAPI, Gemini, OpenAI} $|$ \href{https://neuroviai.com}{neuroviai.com}
\begin{itemize}
\item Architected multi-model cascade: Gemini primary $\rightarrow$ OpenAI fallback $\rightarrow$ structured JSON validator.
\item Wrote 15+ prompt templates with variable injection, few-shot examples, and temperature/top-p tuning.
\item Built image-generation pipeline converting text briefs into social-media visuals at production scale.
\item Designed token-economy backend: per-user quota tracking, usage alerts, and Razorpay billing hooks.
\item Implemented quality-scoring heuristic that auto-flags low-confidence outputs for human review.
\end{itemize}

\textbf{Agentic Virtual Therapist} $|$ \textit{LangGraph, Python} $|$ \href{https://github.com/JeetInTech/Virtual-Therapist---LangGraph-Agentic-AI-System}{GitHub} \hfill Sep--Oct 2025
\begin{itemize}
\item Built 3-agent LangGraph system: intake, emotion detector, response generator with state handoff.
\item Integrated speech-to-text and adaptive LLM replies tuned to detected emotional context.
\end{itemize}

\textbf{IntelliSense Analytics} $|$ \textit{Pandas, Scikit-learn} \hfill Apr--Jun 2025
\begin{itemize}
\item Automated feature engineering and trend forecasting across heterogeneous datasets.
\end{itemize}

\section*{EXPERIENCE}
\textbf{Inikola Technologies -- Data Science Intern} \hfill Mar 2025 -- Present
\begin{itemize}
\item Deployed NLP inference pipelines into CraftingBrain's production backend for real-time text processing.
\item Iterated on prompt strategies, cutting content-generation latency while maintaining output quality.
\item Built data-ingestion scripts processing structured and unstructured sources into model-ready format.
\end{itemize}

\textbf{Freelance AI Developer} \hfill Nov 2024 -- Present
\begin{itemize}
\item Shipped RAG search, chatbot, and content-automation products for early-stage startups.
\item Managed LLM provider costs through quota splitting, caching, and request batching strategies.
\item Created evaluation harnesses measuring output relevance, factuality, and token efficiency.
\end{itemize}

\section*{EDUCATION}
\textbf{B.Tech, AI \& Machine Learning} -- Malla Reddy University \hfill Expected 2026 \hfill GPA: 8.0/10

\section*{RESEARCH \& AWARDS}
IEEE Research Paper (AI Systems) $|$ 1st Place IDEATHON 2.0 $|$ METALLOOP 2K23 \\
\textit{Certs:} Google Cloud, AWS, Coursera (ML), Microsoft Learn, NPTEL

\end{document}
