\documentclass[10pt]{article}
\usepackage[margin=0.4in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\setlist[itemize]{leftmargin=*, noitemsep, topsep=2pt, parsep=0pt}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\titlespacing{\section}{0pt}{6pt}{3pt}
\hypersetup{hidelinks}

\begin{document}

\begin{center}
{\Large \textbf{SANGRAMJEET GHOSH}} \\[2pt]
{\small +91 9059150937 $|$ sangramjeet47@gmail.com $|$
\href{https://www.linkedin.com/in/sangramjeetghosh}{linkedin.com/in/sangramjeetghosh} $|$
\href{https://github.com/JeetInTech}{github.com/JeetInTech} $|$
\href{https://neuroviai.com}{neuroviai.com}}
\end{center}

\noindent\rule{\textwidth}{0.4pt}

\section*{SUMMARY}
SaaS Product Engineer who has been through the full product lifecycle---ideation, architecture, development, payment integration, launch, and iteration. Solo-shipped a live AI SaaS with Razorpay subscriptions, token-based billing, user onboarding, analytics dashboards, and multi-platform publishing. Thinks in user journeys, not just code.

\section*{PRODUCT \& TECHNICAL SKILLS}
\textbf{SaaS:} Subscription Management, Tiered Pricing, Token Economy, User Onboarding, Feature Flags \\
\textbf{Payments:} Razorpay (Checkout, Subscriptions, Webhooks, Refunds), Billing Logic, Invoice Generation \\
\textbf{Auth:} JWT, OAuth 2.0, RBAC, Multi-Tenant Session Management \\
\textbf{Stack:} Next.js 14, TypeScript, FastAPI, PostgreSQL, Supabase, Tailwind CSS, Docker

\section*{PRODUCT I SHIPPED}
\textbf{Neuroviai -- AI Content Automation SaaS} $|$ \href{https://neuroviai.com}{neuroviai.com}
\begin{itemize}
\item Took product from zero to live: defined user personas, mapped user journeys, designed DB schema, wrote code, launched.
\item Built Razorpay integration end-to-end: plan creation API, checkout UI, webhook listener, payment ledger, refund flow.
\item Designed token economy: users buy credit packs, each AI action deducts tokens, low-balance alerts trigger upsell.
\item Created onboarding wizard guiding new users through account setup, platform linking, and first content generation.
\item Built analytics dashboard showing engagement metrics, content performance, and publishing history.
\item Integrated 8 APIs (LinkedIn, Twitter/X, Gemini) enabling one-click cross-platform content publishing.
\end{itemize}

\textbf{CvForge -- Resume Builder} $|$ \href{https://github.com/JeetInTech/CvForge-Online}{GitHub}
\begin{itemize}
\item Built self-service product: template picker, drag-and-drop editor, real-time preview, one-click PDF export.
\item Designed UX flow for non-technical users---minimal clicks from signup to finished resume.
\end{itemize}

\section*{EXPERIENCE}
\textbf{Inikola Technologies -- Data Science Intern} \hfill Mar 2025 -- Present
\begin{itemize}
\item Developed backend features for CraftingBrain using Python/FastAPI with focus on user-facing product value.
\item Contributed to product launch readiness: performance testing, bug triage, and user-feedback incorporation.
\item Implemented analytics event tracking to measure feature adoption and user retention signals.
\end{itemize}

\textbf{Freelance Product Developer} \hfill Nov 2024 -- Present
\begin{itemize}
\item Built SaaS MVPs for startup founders: scoping features, setting up billing, launching to first paying users.
\item Owned full product delivery: requirements $\rightarrow$ wireframes $\rightarrow$ code $\rightarrow$ deploy $\rightarrow$ iterate on feedback.
\item Integrated payment gateways, email notification systems, and role-based access into every product.
\end{itemize}

\section*{EDUCATION}
\textbf{B.Tech, AI \& Machine Learning} -- Malla Reddy University \hfill Expected 2026 \hfill GPA: 8.0/10

\section*{AWARDS \& CERTS}
1st Place IDEATHON 2.0 $|$ METALLOOP 2K23 Hackathon $|$ IEEE Paper \\
Coursera, Microsoft Learn, Google Cloud, NPTEL, AWS

\end{document}
