\documentclass[10pt]{article}
\usepackage[margin=0.4in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\setlist[itemize]{leftmargin=*, noitemsep, topsep=2pt, parsep=0pt}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\titlespacing{\section}{0pt}{6pt}{3pt}
\hypersetup{hidelinks}

\begin{document}

\begin{center}
{\Large \textbf{SANGRAMJEET GHOSH}} \\[2pt]
{\small +91 9059150937 $|$ sangramjeet47@gmail.com $|$
\href{https://www.linkedin.com/in/sangramjeetghosh}{linkedin.com/in/sangramjeetghosh} $|$
\href{https://github.com/JeetInTech}{github.com/JeetInTech} $|$
\href{https://neuroviai.com}{neuroviai.com}}
\end{center}

\noindent\rule{\textwidth}{0.4pt}

\section*{OBJECTIVE}
Junior AI/ML Engineer focused on deploying language models and NLP pipelines into production applications---not just notebooks. Published IEEE paper. Built multi-model routing, RAG retrieval, prompt-engineering workflows, and image generation pipelines powering a live SaaS product used by real customers.

\section*{AI \& ML SKILLS}
\textbf{LLM \& NLP:} Prompt Engineering, Multi-Model Cascade, RAG, Embeddings, Transformers, Tokenization \\
\textbf{Frameworks:} LangGraph, LangChain, OpenAI API, Google Gemini API, Hugging Face, Scikit-learn \\
\textbf{Data:} Pandas, NumPy, Matplotlib, Feature Engineering, EDA, PostgreSQL, Vector Search \\
\textbf{Infra:} Python, FastAPI, Docker, AWS, Git, CI/CD

\section*{EXPERIENCE}
\textbf{Inikola Technologies -- Data Science Intern} \hfill Mar 2025 -- Present
\begin{itemize}
\item Deployed transformer-based NLP models into CraftingBrain's production pipeline for real-time text analysis.
\item Tuned prompts (temperature, top-p, system instructions) to improve content-generation accuracy by measurable margins.
\item Wrote ETL scripts in Pandas for structured and unstructured datasets feeding the ML feature store.
\end{itemize}

\textbf{Freelance AI/ML Developer} \hfill Nov 2024 -- Present
\begin{itemize}
\item Shipped RAG-powered search for a startup: embedding generation, HNSW vector index, contextual reranking.
\item Implemented multi-provider LLM routing (OpenAI $\rightarrow$ Gemini fallback) with per-provider quota tracking.
\item Delivered sentiment analysis and content-scoring models to automate editorial review queues.
\end{itemize}

\section*{PROJECTS}
\textbf{Neuroviai -- AI Content Engine} $|$ \textit{Python, FastAPI, Gemini, OpenAI} $|$ \href{https://neuroviai.com}{neuroviai.com}
\begin{itemize}
\item Engineered multi-model cascade: primary Gemini call, OpenAI fallback, structured JSON output parsing.
\item Built prompt templates with variable injection, context windowing, and output-quality scoring heuristics.
\item Created image-generation pipeline producing social-media visuals from text prompts at scale.
\item Designed token-economy backend tracking per-user LLM consumption, quota alerts, and billing hooks.
\end{itemize}

\textbf{Agentic AI Virtual Therapist} $|$ \textit{LangGraph, Python} $|$ \href{https://github.com/JeetInTech/Virtual-Therapist---LangGraph-Agentic-AI-System}{GitHub} \hfill Sep--Oct 2025
\begin{itemize}
\item Orchestrated multi-agent graph: intake agent, emotion-detector agent, and response-generator agent.
\item Integrated speech-to-text for voice input and adaptive LLM responses based on detected emotional state.
\end{itemize}

\textbf{IntelliSense Analytics} $|$ \textit{Pandas, Scikit-learn, Matplotlib} \hfill Apr--Jun 2025
\begin{itemize}
\item Automated data cleaning, feature engineering, and trend forecasting across variable-size datasets.
\end{itemize}

\section*{EDUCATION}
\textbf{B.Tech, AI \& Machine Learning} -- Malla Reddy University \hfill Expected 2026 \hfill GPA: 8.0/10

\section*{PUBLICATIONS \& AWARDS}
IEEE Research Paper (AI Systems) $|$ 1st Place IDEATHON 2.0 $|$ METALLOOP 2K23 National Hackathon \\
\textit{Certs:} Google Cloud, AWS, Coursera (ML Specialization), NPTEL, Microsoft Learn

\end{document}
