\documentclass[10pt]{article}
\usepackage[margin=0.4in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\setlist[itemize]{leftmargin=*, noitemsep, topsep=2pt, parsep=0pt}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\titlespacing{\section}{0pt}{6pt}{3pt}
\hypersetup{hidelinks}

\begin{document}

\begin{center}
{\Large \textbf{SANGRAMJEET GHOSH}} \\[2pt]
{\small +91 9059150937 $|$ sangramjeet47@gmail.com $|$
\href{https://www.linkedin.com/in/sangramjeetghosh}{linkedin.com/in/sangramjeetghosh} $|$
\href{https://github.com/JeetInTech}{github.com/JeetInTech} $|$
\href{https://neuroviai.com}{neuroviai.com}}
\end{center}

\noindent\rule{\textwidth}{0.4pt}

\section*{PROFILE}
Junior DevOps \& Cloud Engineer who deploys and operates multi-service applications across AWS, Render, Netlify, and Supabase. Hands-on with Docker containerization, GitHub Actions CI/CD, environment management, and SSL/DNS configuration. Independently shipped a microservices SaaS platform across 4 cloud providers with automated build-test-deploy pipelines.

\section*{DEVOPS \& CLOUD SKILLS}
\textbf{Cloud:} AWS (EC2, S3, IAM), Render, Netlify, Supabase, Vercel \\
\textbf{Containers:} Docker, Docker Compose, Multi-Stage Builds, Container Networking \\
\textbf{CI/CD:} GitHub Actions, Automated Build Pipelines, Rollback Strategies \\
\textbf{Infra:} Environment Vars, Secrets Management, SSL/TLS, DNS, CDN, Health Checks \\
\textbf{Scripting:} Python, Bash/Shell, SQL, Git branching strategies

\section*{EXPERIENCE}
\textbf{Inikola Technologies -- Data Science Intern} \hfill Mar 2025 -- Present
\begin{itemize}
\item Owned AWS deployment of CraftingBrain production site: EC2 provisioning, S3 static assets, IAM policies.
\item Wrote Dockerfiles with multi-stage builds cutting image size by 40\%; added health-check probes.
\item Created GitHub Actions workflow: lint $\rightarrow$ test $\rightarrow$ build $\rightarrow$ deploy with Slack notification on failure.
\end{itemize}

\textbf{Freelance DevOps \& Web Developer} \hfill Nov 2024 -- Present
\begin{itemize}
\item Deployed 3+ client apps across Render, Netlify, and Supabase with zero-downtime rolling updates.
\item Configured custom domains, Let's Encrypt SSL, Cloudflare DNS, and CDN caching rules.
\item Set up per-environment .env management (dev/staging/prod) with secret injection at build time.
\end{itemize}

\section*{INFRASTRUCTURE PROJECTS}
\textbf{Neuroviai -- Multi-Cloud SaaS Deployment} $|$ \href{https://neuroviai.com}{neuroviai.com}
\begin{itemize}
\item Deployed 4 microservices (auth, content, payment, AI) across AWS + Render + Supabase + Netlify.
\item Wrote Docker Compose for local dev that mirrors production topology; single \texttt{docker compose up} spin-up.
\item Built GitHub Actions matrix pipeline: parallel lint + test, sequential Docker build + push + deploy.
\item Managed API-key rotation, webhook secret hashing, and environment-variable templates across services.
\item Configured uptime monitoring, structured JSON logging, and automated Slack alerts on 5xx spikes.
\end{itemize}

\textbf{CraftingBrain -- Production Deployment} $|$ \textit{AWS, Docker} $|$ \href{https://craftingbrain.com}{craftingbrain.com}
\begin{itemize}
\item Provisioned EC2 instance, configured Nginx reverse proxy, and set up automated daily database backups.
\end{itemize}

\textbf{Therapy AI -- Container Orchestration} $|$ \textit{Docker Compose} $|$ \href{https://github.com/JeetInTech/Virtual-Therapist---LangGraph-Agentic-AI-System}{GitHub} \hfill Sep--Oct 2025
\begin{itemize}
\item Containerized multi-service AI app with inter-container networking and shared volume mounts.
\end{itemize}

\section*{EDUCATION}
\textbf{B.Tech, AI \& Machine Learning} -- Malla Reddy University \hfill Expected 2026 \hfill GPA: 8.0/10

\section*{CERTIFICATIONS \& AWARDS}
AWS $|$ Google Cloud $|$ Coursera $|$ Microsoft Learn $|$ NPTEL \\
1st Place IDEATHON 2.0 $|$ METALLOOP 2K23 National Hackathon $|$ IEEE Research Paper

\end{document}
