\documentclass[10pt]{article}
\usepackage[margin=0.4in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\setlist[itemize]{leftmargin=*, noitemsep, topsep=2pt, parsep=0pt}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\titlespacing{\section}{0pt}{6pt}{3pt}
\hypersetup{hidelinks}

\begin{document}

\begin{center}
{\Large \textbf{SANGRAMJEET GHOSH}} \\[2pt]
{\small +91 9059150937 $|$ sangramjeet47@gmail.com $|$
\href{https://www.linkedin.com/in/sangramjeetghosh}{linkedin.com/in/sangramjeetghosh} $|$
\href{https://github.com/JeetInTech}{github.com/JeetInTech} $|$
\href{https://neuroviai.com}{neuroviai.com}}
\end{center}

\noindent\rule{\textwidth}{0.4pt}

\section*{PROFILE}
Solutions Engineer who bridges deep technical ability with clear communication. Published IEEE researcher, technical writer, and builder who has integrated 8 APIs, documented system architectures, and consulted startup founders on tech decisions. Equally comfortable writing Python backend code and writing integration guides that a junior dev can follow.

\section*{SKILLS}
\textbf{Technical Depth:} Python, FastAPI, Next.js, PostgreSQL, REST APIs, Microservices, AI/LLM Integration \\
\textbf{Documentation:} API Specs (OpenAPI/Swagger), System Architecture Diagrams, Integration Guides \\
\textbf{Communication:} Technical Writing, Client Requirement Analysis, Stakeholder Presentations \\
\textbf{Tools:} Git, Docker, AWS, Postman, Markdown, Notion

\section*{PUBLICATION}
\textbf{IEEE Research Paper} -- Peer-reviewed publication on AI systems. Demonstrates structured analysis, academic writing rigour, and ability to communicate complex findings to a technical audience.

\section*{EXPERIENCE}
\textbf{Inikola Technologies -- Data Science Intern} \hfill Mar 2025 -- Present
\begin{itemize}
\item Built FastAPI services for CraftingBrain and authored Swagger-documented API specs for each endpoint.
\item Wrote internal wiki pages covering deployment procedures, troubleshooting steps, and architecture decisions.
\item Presented technical proposals to the team lead, translating product requirements into implementation plans.
\end{itemize}

\textbf{Freelance Solutions Developer} \hfill Nov 2024 -- Present
\begin{itemize}
\item Consulted with 3+ startup founders: scoped technical feasibility, proposed architectures, delivered working MVPs.
\item Created integration runbooks (Razorpay, LinkedIn API, Twitter/X) that clients' in-house devs used post-handoff.
\item Built proof-of-concept demos to validate technical approaches before committing to full implementation.
\end{itemize}

\section*{SOLUTION PROJECTS}
\textbf{Neuroviai -- AI SaaS Platform} $|$ \href{https://neuroviai.com}{neuroviai.com}
\begin{itemize}
\item Designed and documented complete system architecture: service boundaries, data flows, and API contracts.
\item Wrote integration guides for 8 external APIs covering auth flows, error codes, rate limits, and edge cases.
\item Created troubleshooting knowledge base for common deployment and integration failure modes.
\item Built the full platform (frontend, backend, AI, payments) to deeply understand every integration point.
\end{itemize}

\textbf{Virtual Therapist Documentation} $|$ \href{https://github.com/JeetInTech/Virtual-Therapist---LangGraph-Agentic-AI-System}{GitHub} \hfill Sep--Oct 2025
\begin{itemize}
\item Authored developer guide: LangGraph agent patterns, prompt templates, and deployment instructions.
\item Documented multi-agent decision trees and state transitions for onboarding new contributors.
\end{itemize}

\textbf{CvForge} $|$ \href{https://github.com/JeetInTech/CvForge-Online}{GitHub}
\begin{itemize}
\item Wrote end-user documentation and developer README with setup instructions and API reference.
\end{itemize}

\section*{EDUCATION}
\textbf{B.Tech, AI \& Machine Learning} -- Malla Reddy University \hfill Expected 2026 \hfill GPA: 8.0/10

\section*{AWARDS \& CERTIFICATIONS}
1st Place IDEATHON 2.0 $|$ METALLOOP 2K23 National Hackathon \\
Coursera, Microsoft Learn, Google Cloud, NPTEL, AWS

\end{document}
