\documentclass[10pt]{article}
\usepackage[margin=0.4in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\setlist[itemize]{leftmargin=*, noitemsep, topsep=2pt, parsep=0pt}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\titlespacing{\section}{0pt}{6pt}{3pt}
\hypersetup{hidelinks}

\begin{document}

\begin{center}
{\Large \textbf{SANGRAMJEET GHOSH}} \\[2pt]
{\small +91 9059150937 $|$ sangramjeet47@gmail.com $|$
\href{https://www.linkedin.com/in/sangramjeetghosh}{linkedin.com/in/sangramjeetghosh} $|$
\href{https://github.com/JeetInTech}{github.com/JeetInTech} $|$
\href{https://neuroviai.com}{neuroviai.com}}
\end{center}

\noindent\rule{\textwidth}{0.4pt}

\section*{PROFILE}
API Developer with production experience orchestrating 8 third-party integrations---LinkedIn, Twitter/X, Razorpay, Google Gemini, OpenAI---inside a live SaaS product. Skilled at designing versioned REST endpoints, wiring OAuth 2.0 handshakes, handling webhooks, enforcing rate limits, and building retry/fallback logic. Strong at writing clear API documentation and integration guides.

\section*{API \& INTEGRATION SKILLS}
\textbf{API Design:} RESTful Endpoints, Versioning, Request/Response Schemas, Pagination, HATEOAS basics \\
\textbf{3rd-Party APIs:} LinkedIn, Twitter/X, Razorpay, Google Gemini, OpenAI, Webhook Receivers \\
\textbf{Auth Protocols:} OAuth 2.0 (Authorization Code + Client Credentials), JWT, API Key Rotation \\
\textbf{Resilience:} Rate Limiting, Retry with Backoff, Circuit Breaker Patterns, Timeout Management \\
\textbf{Stack:} Python, FastAPI, PostgreSQL, Postman, Docker, Git

\section*{PROJECTS}
\textbf{Neuroviai -- 8-API SaaS Platform} $|$ \textit{FastAPI, PostgreSQL} $|$ \href{https://neuroviai.com}{neuroviai.com}
\begin{itemize}
\item Wired LinkedIn and Twitter/X publishing APIs end-to-end: OAuth consent, token refresh, post creation, analytics pull.
\item Built Razorpay payment integration: plan creation, checkout sessions, webhook signature verification, refund API.
\item Orchestrated Google Gemini and OpenAI calls through a unified gateway with provider-level quota tracking.
\item Designed internal REST API surface (20+ endpoints) for user management, scheduling, and content CRUD.
\end{itemize}

\textbf{Virtual Therapy AI} $|$ \textit{Python, LangGraph, LLM APIs} $|$ \href{https://github.com/JeetInTech/Virtual-Therapist---LangGraph-Agentic-AI-System}{GitHub} \hfill Sep--Oct 2025
\begin{itemize}
\item Chained speech-to-text API and LLM inference API with async request pipeline and structured JSON output.
\item Implemented multi-provider fallback: if primary LLM timed out, request routed to secondary within 200ms.
\end{itemize}

\textbf{CvForge -- Resume Builder API} $|$ \textit{FastAPI, JavaScript} $|$ \href{https://github.com/JeetInTech/CvForge-Online}{GitHub}
\begin{itemize}
\item Defined REST contract for resume CRUD, template selection, and PDF export with Swagger auto-docs.
\end{itemize}

\section*{EXPERIENCE}
\textbf{Inikola Technologies -- Data Science Intern} \hfill Mar 2025 -- Present
\begin{itemize}
\item Authored RESTful endpoints for CraftingBrain's content platform; wrote Postman collections and integration tests.
\item Plugged external NLP APIs into the service layer and exposed processed results through versioned REST routes.
\item Set up request validation middleware returning RFC 7807 problem-detail error objects.
\end{itemize}

\textbf{Freelance API Developer} \hfill Nov 2024 -- Present
\begin{itemize}
\item Delivered API backends for 3+ clients: scoped endpoints, wrote OpenAPI specs, handled change requests.
\item Built webhook listeners for payment confirmations, social-media callbacks, and event-driven workflows.
\item Created runnable Postman workspaces and Markdown integration guides as part of every handoff.
\end{itemize}

\section*{EDUCATION}
\textbf{B.Tech, AI \& Machine Learning} -- Malla Reddy University \hfill Expected 2026 \hfill GPA: 8.0/10

\section*{HIGHLIGHTS}
IEEE Research Paper $|$ 1st Place IDEATHON 2.0 $|$ METALLOOP 2K23 Hackathon \\
\textit{Certs:} AWS, Google Cloud, Coursera, Microsoft Learn, NPTEL

\end{document}
