\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{fontawesome5}
\usepackage{ulem} % for underline styling

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{10pt}
\hypersetup{colorlinks=true, urlcolor=blue!70!black}

\newcommand{\blank}[1]{\underline{\hspace{#1}}}

\begin{document}

% ============================================================
%  COLD EMAIL TEMPLATE — Copy the text below into your email
% ============================================================

\begin{center}
{\large \textbf{COLD EMAIL TEMPLATE}} \\[4pt]
{\small \textit{Copy into Gmail / Outlook. Fill in the blanks. Attach your role-specific resume.}}
\end{center}

\noindent\rule{\textwidth}{0.6pt}

\vspace{6pt}

% ----- SUBJECT LINE -----
\textbf{Subject:} \blank{3cm} (Role Title) — AI \& Full-Stack Developer | B.Tech 2026

\vspace{4pt}
\noindent\rule{\textwidth}{0.2pt}
\vspace{4pt}

% ----- EMAIL BODY -----
Hi \blank{3cm} (Hiring Manager / Recruiter Name),

I hope this email finds you well. My name is Sangramjeet Ghosh, and I'm reaching out because I'm genuinely excited about the work \blank{4cm} (Company Name) is doing in \blank{4cm} (specific area — e.g., ``AI-powered logistics,'' ``developer tooling,'' ``content automation'').

I'm a pre-final year B.Tech student (AI \& ML, Malla Reddy University, GPA 8.0/10) who has been building and shipping production software for the past year. A few things that might be relevant to your team:

\begin{itemize}
\setlength{\itemsep}{4pt}
\item \textbf{Shipped a live SaaS} — I built \href{https://neuroviai.com}{Neuroviai}, an AI content-automation platform with multi-model LLM orchestration, Razorpay payments, and 8 API integrations. It's live and serving users.
\item \textbf{Production experience} — Currently a Data Science Intern at Inikola Technologies, where I build NLP pipelines, manage AWS infrastructure, and run CI/CD for \href{https://craftingbrain.com}{CraftingBrain}.
\item \textbf{Research} — Published a peer-reviewed paper in IEEE on AI systems.
\item \textbf{\blank{4cm}} (Add 1 bullet specific to THIS company — e.g., ``Built a LangGraph multi-agent system, relevant to your conversational AI product'')
\end{itemize}

I noticed \blank{5cm} (something specific about the company — a recent blog post, product launch, open-source project, job listing, LinkedIn post, etc.). I'd love to contribute to \blank{4cm} (specific team / product / problem).

I'm open to \blank{4cm} (internship / full-time / part-time / contract) roles in \blank{4cm} (backend / full-stack / AI-ML / DevOps — match to the resume you're attaching). I've attached my resume for reference.

Would you be open to a brief 15-minute call or chat? I'm flexible on timing and happy to work around your schedule.

\vspace{6pt}

Thank you for your time!

\vspace{14pt}

Best regards, \\[2pt]
\textbf{Sangramjeet Ghosh} \\
\faPhone\ +91 9059150937 \\
\faEnvelope\ \href{mailto:sangramjeet47@gmail.com}{sangramjeet47@gmail.com} \\
\faLinkedin\ \href{https://www.linkedin.com/in/sangramjeetghosh}{linkedin.com/in/sangramjeetghosh} \\
\faGithub\ \href{https://github.com/JeetInTech}{github.com/JeetInTech} \\
\faGlobe\ \href{https://neuroviai.com}{neuroviai.com} \\
\faFolder\ \href{https://drive.google.com/drive/folders/1ZQd-DeX-rXlEVDTwDJfjLjnG7iPc_fEw}{Certificate Portfolio}

\vspace{20pt}
\noindent\rule{\textwidth}{0.6pt}

% ============================================================
%  FOLLOW-UP EMAIL (send 4-5 days later if no reply)
% ============================================================

\begin{center}
{\large \textbf{FOLLOW-UP EMAIL}} \\[4pt]
{\small \textit{Send 4--5 business days after the first email if you don't hear back.}}
\end{center}

\noindent\rule{\textwidth}{0.2pt}

\vspace{6pt}

\textbf{Subject:} Re: \blank{3cm} (Role Title) — Quick follow-up

\vspace{4pt}
\noindent\rule{\textwidth}{0.2pt}
\vspace{4pt}

Hi \blank{3cm} (Same name as above),

Just following up on my previous email regarding \blank{3cm} (role / opportunity) at \blank{3cm} (Company Name). I understand you're busy, so I'll keep this brief.

Since my last email, \blank{5cm} (mention something new — e.g., ``I shipped a new feature on Neuroviai,'' ``completed an AWS certification,'' or ``built a prototype relevant to your product''). Happy to share details if helpful.

I remain very interested in contributing to your team. Would a quick 10-minute chat work sometime this week?

\vspace{14pt}

Best, \\[2pt]
\textbf{Sangramjeet Ghosh} \\
\href{mailto:sangramjeet47@gmail.com}{sangramjeet47@gmail.com} $|$ +91 9059150937

\vspace{20pt}
\noindent\rule{\textwidth}{0.6pt}

% ============================================================
%  TIPS
% ============================================================

\begin{center}
{\large \textbf{COLD EMAIL TIPS}}
\end{center}

\begin{enumerate}
\setlength{\itemsep}{4pt}
\item \textbf{Find the right person} — Target engineering managers, tech leads, or team-specific recruiters. Avoid generic ``careers@'' addresses.
\item \textbf{Personalize every email} — Mention something specific about the company (blog post, product, GitHub repo, LinkedIn post). Generic emails get ignored.
\item \textbf{Keep it short} — Aim for 150--200 words in the body. Recruiters skim.
\item \textbf{Attach the right resume} — Use the role-specific resume from your ATS folder that matches the position.
\item \textbf{Subject line matters} — Include the role title and one differentiator (``AI \& Full-Stack Developer'' or ``IEEE-Published ML Engineer'').
\item \textbf{Send Tuesday--Thursday, 8--10 AM} in the recipient's timezone for best open rates.
\item \textbf{Follow up once} after 4--5 business days. Don't send more than 2 emails total.
\item \textbf{Use LinkedIn too} — Connect with a short note referencing your email for a multi-touch approach.
\end{enumerate}

\end{document}
