\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{fontawesome5}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{10pt}
\hypersetup{colorlinks=true, urlcolor=blue!70!black}

\begin{document}

% ===== HEADER =====
\begin{center}
{\Large \textbf{SANGRAMJEET GHOSH}} \\[6pt]
{\small
\faPhone\ +91 9059150937 \quad $|$ \quad
\faEnvelope\ \href{mailto:sangramjeet47@gmail.com}{sangramjeet47@gmail.com} \quad $|$ \quad
\faLinkedin\ \href{https://www.linkedin.com/in/sangramjeetghosh}{linkedin.com/in/sangramjeetghosh}
}\\[2pt]
{\small
\faGithub\ \href{https://github.com/JeetInTech}{github.com/JeetInTech} \quad $|$ \quad
\faGlobe\ \href{https://neuroviai.com}{neuroviai.com}
}
\end{center}

\vspace{10pt}

\noindent \today

\vspace{6pt}

\noindent Dear Hiring Manager,

I am writing to express my interest in the open position at your organization. As a B.Tech student in Artificial Intelligence \& Machine Learning at Malla Reddy University (expected 2026, GPA 8.0/10), I bring a combination of strong academic grounding and real-world product-building experience that I believe would be valuable to your team.

Over the past year, I have gone beyond coursework to build and ship production software. My most significant project is \textbf{Neuroviai} (\href{https://neuroviai.com}{neuroviai.com})---a live AI-powered SaaS platform I designed, developed, and deployed end-to-end. It features multi-provider LLM orchestration, 8 third-party API integrations (LinkedIn, Twitter/X, Razorpay, and others), subscription billing, and a microservice architecture deployed across AWS, Render, and Supabase. Building Neuroviai taught me how to make architectural trade-offs, debug production issues, manage API rate limits, and ship features that real users depend on.

As a \textbf{Data Science Intern at Inikola Technologies}, I contribute to CraftingBrain (\href{https://craftingbrain.com}{craftingbrain.com}), a live content-technology platform, where I build NLP pipelines, manage AWS infrastructure, and maintain CI/CD workflows. In parallel, my \textbf{freelance practice} has given me experience delivering MVPs for startup founders---from requirements scoping through deployment and handoff.

A few highlights that reflect the range of what I can contribute:

\begin{itemize}
\setlength{\itemsep}{4pt}
\item Built and shipped a full-stack SaaS with AI content generation, payment processing, and social-media publishing.
\item Designed multi-agent AI systems using LangGraph and LangChain with state-based orchestration.
\item Published a peer-reviewed paper in IEEE on applied AI systems.
\item Won 1st Place at IDEATHON 2.0 (national-level) and competed at METALLOOP 2K23 national hackathon.
\item Hold certifications from AWS, Google Cloud, Coursera, Microsoft Learn, and NPTEL.
\end{itemize}

I am drawn to roles where I can solve meaningful problems with code, learn from experienced engineers, and contribute to products that matter. I am comfortable working across the stack---from training ML models to configuring Nginx---and I thrive in fast-paced environments where shipping quality work quickly is valued.

I would welcome the opportunity to discuss how my skills and experience align with your team's needs. My resume is attached for your review, and my complete certificate portfolio is available at \href{https://drive.google.com/drive/folders/1ZQd-DeX-rXlEVDTwDJfjLjnG7iPc_fEw}{this link}.

Thank you for your time and consideration.

\vspace{20pt}

\noindent Sincerely, \\[4pt]
\textbf{Sangramjeet Ghosh} \\
\href{mailto:sangramjeet47@gmail.com}{sangramjeet47@gmail.com} \quad $|$ \quad +91 9059150937

\end{document}
