\documentclass[10pt]{article}
\usepackage[margin=0.4in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\setlist[itemize]{leftmargin=*, noitemsep, topsep=2pt, parsep=0pt}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\titlespacing{\section}{0pt}{6pt}{3pt}
\hypersetup{hidelinks}

\begin{document}

\begin{center}
{\Large \textbf{SANGRAMJEET GHOSH}} \\[2pt]
{\small +91 9059150937 $|$ sangramjeet47@gmail.com $|$
\href{https://www.linkedin.com/in/sangramjeetghosh}{linkedin.com/in/sangramjeetghosh} $|$
\href{https://github.com/JeetInTech}{github.com/JeetInTech} $|$
\href{https://neuroviai.com}{neuroviai.com}}
\end{center}

\noindent\rule{\textwidth}{0.4pt}

\section*{SUMMARY}
Full-Stack Developer who ships end-to-end web products using Next.js 14 on the frontend and Python/FastAPI on the backend. Comfortable owning the entire stack---responsive UI, REST APIs, database modelling, auth, payments, and cloud deployment. Solo-launched a live AI SaaS platform with Razorpay billing and 8 external integrations.

\section*{TECHNICAL SKILLS}
\textbf{Frontend:} React, Next.js 14, TypeScript, Tailwind CSS, Zustand, HTML5, Responsive \& Mobile-First Design \\
\textbf{Backend:} Python, FastAPI, REST APIs, JWT/OAuth 2.0, Webhook Handling \\
\textbf{Databases:} PostgreSQL, Supabase, MySQL, Schema Design, Query Tuning \\
\textbf{Tooling:} Docker, AWS, Render, Netlify, Capacitor (Mobile), Git, CI/CD

\section*{PROJECTS}
\textbf{Neuroviai -- AI SaaS Platform} $|$ \textit{Next.js 14, FastAPI, PostgreSQL, Supabase} $|$ \href{https://neuroviai.com}{neuroviai.com}
\begin{itemize}
\item Solo-built a production SaaS from scratch: Next.js SSR frontend, FastAPI microservices, PostgreSQL data layer.
\item Coded responsive dashboard with analytics charts, content calendar, and multi-platform publisher.
\item Integrated Razorpay subscriptions, token-based billing, and 8 APIs (LinkedIn, Twitter/X, Gemini, OpenAI).
\item Shipped Capacitor mobile build maintaining feature parity with the web version.
\end{itemize}

\textbf{CvForge -- Resume Builder} $|$ \textit{JavaScript, FastAPI, HTML/CSS} $|$ \href{https://github.com/JeetInTech/CvForge-Online}{GitHub}
\begin{itemize}
\item Created full-stack app with dynamic form handling, live preview, template switching, and PDF export.
\item Designed REST endpoints for data persistence, template rendering, and validation logic.
\end{itemize}

\textbf{Virtual Therapist} $|$ \textit{React, Python, LangGraph} $|$ \href{https://github.com/JeetInTech/Virtual-Therapist---LangGraph-Agentic-AI-System}{GitHub} \hfill Sep--Oct 2025
\begin{itemize}
\item Delivered chat UI with streaming responses, typing indicators, and speech-to-text input.
\item Wired LangGraph orchestration backend to React frontend over async REST endpoints.
\end{itemize}

\section*{EXPERIENCE}
\textbf{Inikola Technologies -- Data Science Intern} \hfill Mar 2025 -- Present
\begin{itemize}
\item Developed full-stack features for CraftingBrain: FastAPI endpoints + React components for content workflows.
\item Deployed production site on AWS with Docker containers and Git-triggered CI/CD pipelines.
\item Integrated NLP text-processing services and surfaced results through interactive frontend views.
\end{itemize}

\textbf{Freelance Full-Stack Developer} \hfill Nov 2024 -- Present
\begin{itemize}
\item Shipped 3+ client projects end-to-end: Next.js frontends, FastAPI backends, PostgreSQL databases.
\item Implemented auth (JWT/OAuth), payment flows, and API-driven features across every engagement.
\item Owned requirements, database modelling, UI design, and production deployment for each project.
\end{itemize}

\section*{EDUCATION}
\textbf{B.Tech, AI \& Machine Learning} -- Malla Reddy University \hfill Expected 2026 \hfill GPA: 8.0/10

\section*{RECOGNITION}
1st Place IDEATHON 2.0 $|$ METALLOOP 2K23 National Hackathon $|$ IEEE Paper Published \\
\textit{Certs:} Coursera, Microsoft Learn, Google Cloud, NPTEL, AWS

\end{document}
