\documentclass[10pt]{article}
\usepackage[margin=0.4in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\setlist[itemize]{leftmargin=*, noitemsep, topsep=2pt, parsep=0pt}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\titlespacing{\section}{0pt}{6pt}{3pt}
\hypersetup{hidelinks}

\begin{document}

\begin{center}
{\Large \textbf{SANGRAMJEET GHOSH}} \\[2pt]
{\small +91 9059150937 $|$ sangramjeet47@gmail.com $|$
\href{https://www.linkedin.com/in/sangramjeetghosh}{linkedin.com/in/sangramjeetghosh} $|$
\href{https://github.com/JeetInTech}{github.com/JeetInTech} $|$
\href{https://neuroviai.com}{neuroviai.com}}
\end{center}

\noindent\rule{\textwidth}{0.4pt}

\section*{SUMMARY}
Python Backend Developer experienced in shipping production REST APIs and microservices with FastAPI. Hands-on with PostgreSQL schema design, JWT/OAuth authentication, payment gateway wiring (Razorpay), and asynchronous request processing. Independently architected and deployed a multi-service SaaS backend handling auth, billing, content pipelines, and 8 third-party API integrations.

\section*{SKILLS}
\textbf{Core:} Python, FastAPI, REST API Design, Microservices, Async/Await, Middleware, Error Handling \\
\textbf{Auth \& Security:} JWT, OAuth 2.0, RBAC, Session Tokens, API Key Management \\
\textbf{Data:} PostgreSQL, Supabase, SQL, Schema Design, Indexing, Query Optimization \\
\textbf{DevOps:} Docker, AWS, Render, GitHub Actions, CI/CD, Environment Management

\section*{EXPERIENCE}
\textbf{Inikola Technologies -- Data Science Intern} \hfill Mar 2025 -- Present
\begin{itemize}
\item Developed FastAPI microservices powering CraftingBrain's content management backend, serving 100+ requests daily.
\item Engineered input validation middleware, structured JSON error responses, and PostgreSQL query layers.
\item Containerized services with Docker; established Git-based CI/CD for staging and production deploys.
\end{itemize}

\textbf{Freelance Backend Developer} \hfill Nov 2024 -- Present
\begin{itemize}
\item Delivered API-first backends for startup clients with JWT auth, Razorpay payments, and webhook receivers.
\item Architected PostgreSQL schemas with migration scripts, composite indexes, and parameterized queries.
\item Wrote structured logging, health-check endpoints, and Postman-based API documentation for each delivery.
\end{itemize}

\section*{PROJECTS}
\textbf{Neuroviai} $|$ \textit{FastAPI, PostgreSQL, Supabase, Docker} $|$ \href{https://neuroviai.com}{neuroviai.com}
\begin{itemize}
\item Designed microservice backend: auth service, content service, payment service, and AI inference service.
\item Wired 8 external APIs (LinkedIn, Twitter/X, Razorpay, Gemini) with token refresh, rate-limit handling, and retries.
\item Implemented Razorpay subscription billing with webhook verification, idempotent transaction logging, and refund flows.
\end{itemize}

\textbf{Virtual Therapy AI} $|$ \textit{Python, LangGraph} $|$ \href{https://github.com/JeetInTech/Virtual-Therapist---LangGraph-Agentic-AI-System}{GitHub} \hfill Sep--Oct 2025
\begin{itemize}
\item Built async FastAPI endpoints for speech-to-text ingestion and LLM-driven response generation.
\item Designed stateful session management with conversation persistence in PostgreSQL.
\end{itemize}

\section*{EDUCATION}
\textbf{B.Tech, AI \& Machine Learning} -- Malla Reddy University \hfill Expected 2026 \hfill GPA: 8.0/10

\section*{EXTRAS}
1st Place, IDEATHON 2.0 $|$ METALLOOP 2K23 Hackathon Recognition $|$ IEEE Research Paper Published \\
\textit{Certs:} AWS, Google Cloud, Coursera (ML, Python), Microsoft Learn, NPTEL

\end{document}
