\documentclass[10pt]{article}
\usepackage[margin=0.4in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\setlist[itemize]{leftmargin=*, noitemsep, topsep=2pt, parsep=0pt}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\titlespacing{\section}{0pt}{6pt}{3pt}
\hypersetup{hidelinks}

\begin{document}

\begin{center}
{\Large \textbf{SANGRAMJEET GHOSH}} \\[2pt]
{\small +91 9059150937 $|$ sangramjeet47@gmail.com $|$
\href{https://www.linkedin.com/in/sangramjeetghosh}{linkedin.com/in/sangramjeetghosh} $|$
\href{https://github.com/JeetInTech}{github.com/JeetInTech} $|$
\href{https://neuroviai.com}{neuroviai.com}}
\end{center}

\noindent\rule{\textwidth}{0.4pt}

\section*{SUMMARY}
MarTech developer who builds the tools marketers use to publish, schedule, and measure social media content. Shipped a Buffer/Hootsuite-style SaaS with AI content generation, LinkedIn \& Twitter/X publishing APIs, engagement analytics, content calendar, and subscription billing. Understands both the social-media API landscape and the marketing workflows that sit on top.

\section*{MARTECH SKILLS}
\textbf{Social APIs:} LinkedIn Publishing \& Analytics API, Twitter/X Post API, OAuth 2.0 Consent Flows \\
\textbf{Marketing:} Content Scheduling, Engagement Analytics, A/B Testing, SEO, Campaign Tracking \\
\textbf{AI Content:} LLM-Powered Post Generation, Image Creation Pipelines, Quality Scoring \\
\textbf{Stack:} Python, FastAPI, Next.js 14, PostgreSQL, Tailwind CSS, Docker, Razorpay

\section*{FLAGSHIP PROJECT}
\textbf{Neuroviai -- AI Social Media Automation SaaS} $|$ \href{https://neuroviai.com}{neuroviai.com}
\begin{itemize}
\item Built a production social-media SaaS (Buffer/Hootsuite alternative) with AI-powered content automation.
\item Integrated LinkedIn API (OAuth consent, post creation, analytics pull) and Twitter/X API (tweet posting, threading).
\item Developed AI content pipeline: text generation via Gemini/OpenAI, image generation, caption optimization.
\item Designed engagement dashboard tracking impressions, clicks, shares, follower trends, and best-posting-time analysis.
\item Built content calendar with drag-and-drop scheduling, queue management, and auto-publish at optimal times.
\item Wired Razorpay subscription billing with tiered plans based on post volume and platform count.
\item Created analytics export feature generating PDF/CSV reports for client-facing campaign summaries.
\end{itemize}

\section*{RELATED PROJECTS}
\textbf{IntelliSense -- Marketing Analytics} $|$ \textit{Pandas, Matplotlib} \hfill Apr--Jun 2025
\begin{itemize}
\item Built data pipeline for marketing datasets: automated cleaning, trend extraction, and visual report generation.
\end{itemize}

\textbf{CraftingBrain -- Content Platform} $|$ \href{https://craftingbrain.com}{craftingbrain.com}
\begin{itemize}
\item Developed NLP content-processing features and engagement-signal analysis for a marketing technology startup.
\end{itemize}

\section*{EXPERIENCE}
\textbf{Inikola Technologies -- Data Science Intern} \hfill Mar 2025 -- Present
\begin{itemize}
\item Built AI content-generation and text-analysis workflows for CraftingBrain's MarTech product.
\item Developed NLP pipelines for automated topic extraction, sentiment scoring, and content optimization.
\item Analyzed platform engagement signals to inform content strategy and scheduling decisions.
\end{itemize}

\textbf{Freelance MarTech Developer} \hfill Nov 2024 -- Present
\begin{itemize}
\item Delivered social-media management tools with scheduling, multi-platform publishing, and analytics views.
\item Built AI-powered content pipelines automating caption writing, hashtag suggestion, and image creation.
\item Integrated payment gateways and subscription systems for marketing SaaS monetization.
\end{itemize}

\section*{EDUCATION}
\textbf{B.Tech, AI \& Machine Learning} -- Malla Reddy University \hfill Expected 2026 \hfill GPA: 8.0/10

\section*{EXTRAS}
Google Ads Certified $|$ 1st Place IDEATHON 2.0 $|$ METALLOOP 2K23 $|$ IEEE Paper \\
\textit{Certs:} Coursera, Microsoft Learn, Google Cloud, NPTEL, AWS

\end{document}
