\documentclass[11pt]{article}
\usepackage[margin=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{fontawesome5}
\usepackage{tabularx}

\setlist[itemize]{leftmargin=*, noitemsep, topsep=3pt, parsep=1pt}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\titlespacing{\section}{0pt}{10pt}{5pt}
\titleformat{\section}{\large\bfseries\scshape}{}{0pt}{}[\titlerule]
\hypersetup{colorlinks=true, linkcolor=blue!70!black, urlcolor=blue!70!black}

\begin{document}

% ===== HEADER =====
\begin{center}
{\LARGE \textbf{SANGRAMJEET GHOSH}} \\[6pt]
{\normalsize
\faPhone\ +91 9059150937 \quad $|$ \quad
\faEnvelope\ \href{mailto:sangramjeet47@gmail.com}{sangramjeet47@gmail.com} \quad $|$ \quad
\faLinkedin\ \href{https://www.linkedin.com/in/sangramjeetghosh}{linkedin.com/in/sangramjeetghosh}
}\\[2pt]
{\normalsize
\faGithub\ \href{https://github.com/JeetInTech}{github.com/JeetInTech} \quad $|$ \quad
\faGlobe\ \href{https://neuroviai.com}{neuroviai.com} \quad $|$ \quad
\faFolder\ \href{https://drive.google.com/drive/folders/1ZQd-DeX-rXlEVDTwDJfjLjnG7iPc_fEw}{Certificates Portfolio}
}
\end{center}

\vspace{2pt}

% ===== PROFESSIONAL SUMMARY =====
\section*{Professional Summary}
Versatile AI \& Full-Stack Engineer with hands-on experience building and shipping production-grade SaaS applications, intelligent automation systems, and data-driven products. Designed and launched \textbf{Neuroviai}---a live AI-powered content-automation SaaS with multi-provider LLM orchestration, payment processing, and social-media API integrations. IEEE-published researcher with a strong foundation in machine learning, distributed systems, and modern web architectures. Proven ability to take products from concept to deployment across cloud platforms (AWS, Render, Supabase, Vercel). Actively seeking opportunities to build impactful technology at scale.

% ===== EDUCATION =====
\section*{Education}
\textbf{Bachelor of Technology (B.Tech), Artificial Intelligence \& Machine Learning} \hfill Expected May 2026 \\
Malla Reddy University, Hyderabad, Telangana \hfill \textbf{GPA: 8.0 / 10.0}

\begin{itemize}
\item \textbf{Relevant Coursework:} Data Structures \& Algorithms, Machine Learning, Deep Learning, Natural Language Processing, Computer Vision, Database Management Systems, Cloud Computing, Software Engineering, Statistics \& Probability
\item \textbf{Academic Focus:} AI/ML system design, applied NLP, full-stack application development
\end{itemize}

% ===== TECHNICAL SKILLS =====
\section*{Technical Skills}

\begin{tabularx}{\textwidth}{@{}l X@{}}
\textbf{Languages} & Python, JavaScript, TypeScript, SQL, HTML5, CSS3, Bash \\[3pt]
\textbf{AI / ML} & LangChain, LangGraph, Transformers (Hugging Face), Scikit-learn, Pandas, NumPy, Matplotlib, OpenAI API, Google Gemini API, RAG Pipelines, Vector Embeddings, Prompt Engineering \\[3pt]
\textbf{Backend} & FastAPI, REST APIs, JWT / OAuth 2.0, Razorpay Integration, Webhook Handlers, Microservices Architecture \\[3pt]
\textbf{Frontend} & React 18, Next.js 14 (App Router), Tailwind CSS, Zustand, ShadCN/UI, Responsive Design \\[3pt]
\textbf{Databases} & PostgreSQL, Supabase, MongoDB (basics), SQLAlchemy ORM \\[3pt]
\textbf{DevOps / Cloud} & AWS (EC2, S3, IAM), Docker, Docker Compose, GitHub Actions CI/CD, Render, Vercel, Netlify, Nginx \\[3pt]
\textbf{Tools} & Git, GitHub, Postman, VS Code, Jupyter, Figma, Notion, Linux CLI \\
\end{tabularx}

% ===== WORK EXPERIENCE =====
\section*{Work Experience}

\textbf{Data Science Intern} \hfill \textit{Mar 2025 -- Present} \\
\textit{Inikola Technologies, Hyderabad}
\begin{itemize}
\item Developing AI-powered backend features for \textbf{CraftingBrain} (\href{https://craftingbrain.com}{craftingbrain.com}), a live content-technology platform, using Python and FastAPI.
\item Building and deploying NLP pipelines for real-time text analysis, sentiment scoring, topic extraction, and content optimization in production environments.
\item Managing cloud infrastructure on AWS: EC2 instance provisioning, S3 bucket policies, IAM role configuration, and Nginx reverse-proxy setup.
\item Containerized Python services using multi-stage Docker builds, reducing image size and cold-start latency.
\item Authored CI/CD pipelines with GitHub Actions automating linting, testing, and zero-downtime production deployments.
\item Wrote internal documentation covering deployment procedures, troubleshooting runbooks, and architecture decision records.
\end{itemize}

\textbf{Freelance Full-Stack \& AI Developer} \hfill \textit{Nov 2024 -- Present} \\
\textit{Remote}
\begin{itemize}
\item Delivered end-to-end web applications and AI-powered MVPs for 3+ startup founders, handling requirements gathering, architecture design, development, deployment, and post-launch iteration.
\item Built SaaS products with subscription billing (Razorpay), role-based access control (JWT/OAuth), and multi-platform API integrations.
\item Deployed client applications across AWS, Render, Vercel, and Netlify with custom domains, SSL certificates, and CDN configuration.
\item Created integration guides and handoff documentation enabling clients' in-house teams to maintain and extend delivered products.
\item Managed LLM provider costs through intelligent quota splitting, response caching, and request batching strategies.
\end{itemize}

% ===== PROJECTS =====
\section*{Projects}

\textbf{Neuroviai -- AI-Powered Social Media Automation SaaS} \hfill \textit{Nov 2024 -- Present} \\
\textit{Next.js 14, FastAPI, PostgreSQL, Supabase, Gemini, OpenAI, Razorpay, Docker} \hfill \href{https://neuroviai.com}{\faGlobe\ neuroviai.com}
\begin{itemize}
\item Designed and built a full-stack AI SaaS platform from scratch---covering product design, database schema, API architecture, AI pipelines, payment integration, and multi-platform publishing.
\item Architected multi-model LLM cascade: Gemini as primary provider $\rightarrow$ OpenAI fallback $\rightarrow$ structured JSON validation layer ensuring consistent output quality.
\item Built AI content pipeline: text generation with 15+ prompt templates, image generation for social-media visuals, quality-scoring heuristic for auto-flagging low-confidence outputs.
\item Integrated 8 external APIs (LinkedIn Publishing, Twitter/X, Gemini, OpenAI, Razorpay, Supabase Auth, and others) with OAuth flows, webhook listeners, error handling, and rate-limit management.
\item Implemented end-to-end Razorpay payment system: tiered subscription plans, checkout UI, webhook-based payment confirmation, billing ledger, and refund processing.
\item Designed token-economy billing: per-user credit tracking, usage alerts, low-balance upsell triggers, and plan-upgrade flows.
\item Built engagement analytics dashboard with content performance metrics, publishing history, and optimal-posting-time recommendations.
\item Deployed as 4 microservices across Render (compute), Supabase (database), Netlify (CDN), and AWS S3 (assets) with GitHub Actions CI/CD.
\end{itemize}

\textbf{CvForge -- Online Resume Builder} \hfill \textit{2024} \\
\textit{Next.js, FastAPI, Tailwind CSS} \hfill \href{https://github.com/JeetInTech/CvForge-Online}{\faGithub\ GitHub}
\begin{itemize}
\item Built a self-service resume builder with template selection, drag-and-drop section editor, real-time Markdown preview, and one-click PDF export.
\item Designed mobile-responsive UI with Tailwind CSS and optimized UX flow so non-technical users can go from signup to finished resume in under 5 minutes.
\item Implemented backend API with FastAPI for template storage, user profile management, and PDF rendering.
\end{itemize}

\textbf{Virtual Therapist -- LangGraph Agentic AI System} \hfill \textit{Sep -- Oct 2025} \\
\textit{LangGraph, LangChain, Python, Speech-to-Text} \hfill \href{https://github.com/JeetInTech/Virtual-Therapist---LangGraph-Agentic-AI-System}{\faGithub\ GitHub}
\begin{itemize}
\item Designed and implemented a 3-agent LangGraph system: intake agent, emotion-detection agent, and therapeutic-response generator with state-based handoff.
\item Integrated speech-to-text input processing and adaptive LLM responses tuned to detected emotional context and conversation history.
\item Authored developer documentation: LangGraph agent patterns, prompt templates, state-transition diagrams, and deployment instructions.
\item Containerized with Docker Compose: service dependencies, shared volumes, network isolation, and environment configuration.
\end{itemize}

\textbf{IntelliSense Analytics -- Automated Data Analysis Engine} \hfill \textit{Apr -- Jun 2025} \\
\textit{Python, Pandas, Scikit-learn, Matplotlib}
\begin{itemize}
\item Built an automated analytics pipeline that ingests heterogeneous datasets, performs cleaning, feature engineering, trend extraction, and generates visual reports.
\item Implemented statistical forecasting and anomaly detection modules for time-series and tabular data.
\item Designed interactive visualizations and exportable PDF/CSV reports for business stakeholders.
\end{itemize}

\textbf{CraftingBrain -- Content Technology Platform} \hfill \textit{Mar 2025 -- Present} \\
\textit{Python, FastAPI, AWS, Docker, Nginx} \hfill \href{https://craftingbrain.com}{\faGlobe\ craftingbrain.com}
\begin{itemize}
\item Contributed to a live production platform as part of the Inikola Technologies team.
\item Provisioned and hardened AWS EC2 infrastructure with Nginx reverse proxy, SSL via Certbot, firewall rules, and daily database backups.
\item Built NLP-powered content processing features including topic extraction, readability scoring, and content-suggestion engine.
\end{itemize}

% ===== PUBLICATIONS =====
\section*{Publications \& Research}
\textbf{IEEE Research Paper} -- Peer-reviewed publication on AI systems. \\
Conducted structured analysis and academic research on applied artificial intelligence, demonstrating ability to formalize technical findings, write for peer review, and contribute to the research community.

% ===== ACHIEVEMENTS & COMPETITIONS =====
\section*{Achievements \& Competitions}
\begin{itemize}
\item \textbf{1st Place -- IDEATHON 2.0} (National-level Ideation Competition): Developed and presented an innovative AI-powered solution, evaluated by industry judges for feasibility, impact, and technical execution.
\item \textbf{METALLOOP 2K23} (National Hackathon): Competed as a finalist in a multi-round hackathon building a working prototype under time constraints.
\item \textbf{IEEE Published Researcher}: Authored and published a peer-reviewed paper on AI systems, accepted into IEEE conference proceedings.
\end{itemize}

% ===== CERTIFICATIONS =====
\section*{Certifications}
\textit{All certificates are verified and available at:} \href{https://drive.google.com/drive/folders/1ZQd-DeX-rXlEVDTwDJfjLjnG7iPc_fEw}{\textbf{Certificate Portfolio (Google Drive)}}

\begin{itemize}
\item \textbf{Amazon Web Services (AWS)} -- Cloud Practitioner Essentials / Foundations
\item \textbf{Google Cloud} -- Cloud Computing Fundamentals
\item \textbf{Coursera} -- Machine Learning Specialization / AI \& Data Science tracks
\item \textbf{Microsoft Learn} -- Azure AI Fundamentals / Developer certifications
\item \textbf{NPTEL} -- Programming and Data Science courses (IIT-certified)
\end{itemize}

% ===== EXTRACURRICULAR =====
\section*{Extracurricular \& Leadership}
\begin{itemize}
\item \textbf{Open-Source Contributor:} Actively maintain public repositories on GitHub (\href{https://github.com/JeetInTech}{github.com/JeetInTech}) with multiple AI, web, and data projects.
\item \textbf{Technical Mentor:} Guide junior students in AI/ML concepts, project development, and hackathon preparation.
\item \textbf{Hackathon Participant:} Regular competitor in national-level hackathons and ideathons; strong track record of building functional prototypes under 24--48 hour deadlines.
\item \textbf{Freelance Consultant:} Advise early-stage startup founders on technology stack selection, architecture design, and MVP scoping.
\end{itemize}

% ===== LANGUAGES =====
\section*{Languages}
English (Professional Proficiency) \quad $|$ \quad Hindi (Native) \quad $|$ \quad Bengali (Native)

% ===== LINKS =====
\section*{Online Profiles \& Portfolio}
\begin{tabularx}{\textwidth}{@{}l X@{}}
\textbf{Portfolio / SaaS} & \href{https://neuroviai.com}{neuroviai.com} \\
\textbf{GitHub} & \href{https://github.com/JeetInTech}{github.com/JeetInTech} \\
\textbf{LinkedIn} & \href{https://www.linkedin.com/in/sangramjeetghosh}{linkedin.com/in/sangramjeetghosh} \\
\textbf{Certificates} & \href{https://drive.google.com/drive/folders/1ZQd-DeX-rXlEVDTwDJfjLjnG7iPc_fEw}{Google Drive -- Certificate Portfolio} \\
\end{tabularx}

\vfill
\begin{center}
\small\textit{References available upon request.}
\end{center}

\end{document}
